Refunctionalization of Abstract Abstract Machines (Functional Pearl)

### 2018-06-28 paper/paper.tex
Grammar

It is worth noting that the continuation class @Kont@ is defined as a list of
frames, where a frame can be considered a representation of reduction context 
in reduction semantics.
An empty list represents empty call stack; otherwise, the head frame in the list
represents the innermost context, and the reduction result of this frame will be used
to fill the ``hole'' of its following element in the list.
We represent frames using the @Frame@ class, which stores the information of a single
call-site, i.e., the information that can be used to resume the interrupted computation.
A @Frame@ constitutes a variable name @x@ to be bound later, and a control component
to which the program may resume, and its environment.

>>>>

It is worth noting that the continuation class @Kont@ is defined as a list of
frames, where a frame can be considered a representation of a reduction context
in reduction semantics.
An empty list represents an empty call stack; otherwise, the head frame in the list
represents the innermost context, and the reduction result of this frame will be used
to fill the ``hole'' of its following element in the list.
We represent frames using the @Frame@ class, which stores the information of a single
call-site, i.e., the information that can be used to resume the interrupted computation.
A @Frame@ constitutes a variable name @x@ to be bound later, and a control component
to which the program may resume, as well as its environment.
